---
title: "Anthropometric measurement standardisation tests"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Anthropometric measurement standardisation tests}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(anthrocheckr)
```

Ensuring the precision and accuracy of measurements is critical when collecting anthropometric data. Anthropometrists are usually tested for precision and accuracy of measurement through standardisation tests performed prior to anthropometric data collection. This package provides functions to calculate inter- and intra-observer technical error of measurement (TEM) to assess precision of measurements.

## What does anthrocheckr do?

`{anthrocheckr}` provides functions for:

1. Calculating standard summaries for intra-observer or inter-observer measurements;

2. Calculating intra-observer or inter-observer technical error of measurement (TEM) for multiple subjects and for multiple measurers/observers;

3. Calculating multiple measurers/observers relative technical error of measurement (relative TEM);

4. Calculating intra-observer total technical error of measurement (total TEM);

5. Calculating coefficient of reliability; and,

6. Calculating bias in measurements/observation against a gold standard.


## Installation

`{anthrocheckr}` is not yet on [CRAN](https://cran.r-project.org) but can be installed from the [nutriverse R Universe](https://nutriverse.r-universe.dev) as follows:

```{r install-r-universe, eval = FALSE}
install.packages(
  "anthrocheckr",
  repos = c('https://nutriverse.r-universe.dev', 'https://cloud.r-project.org')
)
```

## Usage